Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-23 paper.qmd
Updated Figure 9 (a)

  ## Compute error
  error_df <- glance(
    df_bin_centroids = df_bin_centroids_scurve,
    df_bin = df_bin_scurve,
    training_data = training_data_scurve,
    newdata = NULL,
    type_NLDR = "UMAP",
    col_start = "x") |>
    mutate(bin1 = xbins,
           bin2 = bin2,
           b = bin1 * bin2,
           b_non_empty = NROW(df_bin_centroids_scurve),
           a1 = a1)

@@

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = a1, 
                         y = MSE)) + 
  geom_point(size = 1) +
  geom_line(linewidth = 0.05) + 
  geom_vline(xintercept = 0.096, linetype=2,
             color = "#bdbdbd", linewidth=1) +
  geom_vline(xintercept = 0.116,
             linetype="solid",
             color = "#bdbdbd",
             linewidth=1) +
  geom_vline(xintercept = 0.184, linetype=2,
             color = "#bdbdbd", linewidth=1) +
  scale_x_continuous(breaks = sort(unique(round(error_scurve$a1, 2)))[c(1, 3, 5, 6, 8, 10:12)]) +
  labs(x = expression(a[1]), y = "MSE") +
  ggtitle("(a)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, 
            angle=90),
        axis.ticks.x = element_line(linewidth = 0.5),
        axis.ticks.y = element_line(linewidth = 0.5),
        plot.title = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10),
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(1, 'cm'),
        legend.key.size = unit(1, 'cm'))

@@

XXX Add tSNE, UMAP, and PaCMAP NLDR layouts and describe what is happening
XXX Discuss the models of one specific cluster (filled out, pancakes): tSNE, UMAP, PaCMAP are useful to capture global structures, but this is an evidence where PaCMAP fail to capture the local structure with default hyper-parameter settings than tSNE and UMAP
XXX Why? hyper-parameter choice specially number of neighbors, data characteristics (intrinsic dimensionality), imbalance between global and local structures, optimization and initialization issues

>>>>

  ## Compute error
  error_df <- glance(
    df_bin_centroids = df_bin_centroids_scurve,
    df_bin = df_bin_scurve,
    training_data = training_data_scurve,
    newdata = NULL,
    type_NLDR = "UMAP",
    col_start = "x") |>
    mutate(bin1 = xbins,
           bin2 = bin2,
           b = bin1 * bin2,
           b_non_empty = NROW(df_bin_centroids_scurve),
           a1 = round(a1, 2))

@@

## Find the minimum MSE when have duplicate a1
error_scurve <- error_scurve |>
  group_by(a1) |>
  filter(MSE == min(MSE)) |>
  ungroup()

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = a1, 
                         y = MSE)) +
  geom_vline(xintercept = 0.10, linetype=2,
           color = "#bdbdbd", linewidth=1) +
  geom_vline(xintercept = 0.12,
             linetype="solid",
             color = "#bdbdbd",
             linewidth=1) +
  geom_vline(xintercept = 0.18, linetype=2,
             color = "#bdbdbd", linewidth=1) +
  geom_line(linewidth = 0.5) + 
  geom_point(size = 1) +
  scale_x_continuous(breaks = sort(unique(round(error_scurve$a1, 2)))[c(1, 3, 5, 6, 8, 10:12)]) +
  labs(x = expression(a[1]), y = "MSE") +
  ggtitle("(a)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5))

@@

XXX Add tSNE, UMAP, and PaCMAP NLDR layouts and describe what is happening
XXX Discuss the models of one specific cluster (filled out, pancakes): tSNE, UMAP, PaCMAP are useful to capture global structures, but this is an evidence where PaCMAP fail to capture the local structure with default hyper-parameter settings than tSNE and UMAP
XXX Why? hyper-parameter choice specially number of neighbors, data characteristics (intrinsic dimensionality), imbalance between global and local structures, optimization and initialization issues
XXX Add this is with specific hyper-parameter choices
